---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cachedChunk, cache=TRUE}
library(data.table)
library(dplyr)
library(ggplot2)
library(highcharter)
library(kableExtra)
library(weights)
library(Hmisc)
library(wordcloud)
#df<-fread("data.csv", header=TRUE, data.table = FALSE, stringsAsFactors = FALSE)
```

# Data Preprocessing
```{r}
#df<-a_df%>%select(SERIALNO,ADJINC,PWGTP,AGEP,CIT,ENG,SEX,MAR,LANP,SCHL,PINCP,RAC1P,RAC2P,SOCP)

#Incorporating adjustment for the Income variable to take into account inflation
df<-df%>%mutate(PINCP=PINCP*(ADJINC/1000000))

#Adding a column to identify age group
df<-df%>%mutate(agegroup=factor(case_when(AGEP >= 65 ~ "Senior",
                                (AGEP >= 25 & AGEP <=64) ~ "Adult",
                                (AGEP >= 15 & AGEP <=24) ~ "Youth",
                                AGEP <=14 ~ "Children")))

#Converting all the categorical variables to factors
df$CIT<-factor(df$CIT, levels=c(1,2,3,4,5), labels=c("Born in US", "Born in Puerto Rico", "Born abroad of American parent(s)", "U.S. citizen by naturalization","Not a citizen of the U.S"))

df$SEX<-factor(df$SEX, levels=c(1,2), labels=c("Male", "Female"))

df$MAR<-factor(df$MAR, levels=c(1,2,3,4,5), labels=c("Married", "Widowed","Divorced","Separated","Single or Under 15"))

df$RAC1P<-factor(df$RAC1P, levels = c(1,2,3,4,5,6,7,8,9), labels = c("White alone","Black or African American alone","American Indian alone","Alaska Native alone","American Indian","Asian alone","Native Hawaiian","Some Other Race","Two or More Races"))

df$ENG<-factor(df$ENG, levels=c(1,2,3,4), labels=c("Very well", "Well", "Not well", "Not at all"))

#Factoring educational attainment
df$SCHL<-factor(df$SCHL, levels =c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24), labels = c("No schooling completed","Nursery school, preschool","Kindergarten","Grade 1", "Grade 2","Grade 3","Grade 4","Grade 5","Grade 6","Grade 7","Grade 8","Grade 9","Grade 10","Grade 11","12th grade - no diploma", "Regular high school diploma","GED or alternative credential","Some college, but less than 1 year","1 or more years of college credit, no degree","Associate's degree","Bachelor's degree","Master's degree","Professional degree beyond a bachelor's degree","Doctorate degree"))

df$RAC2P<-factor(df$RAC2P,levels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68),labels=c("White alone","Black or African American alone","Apache alone","Blackfeet alone","Cherokee alone","Cheyenne alone","Chickasaw alone","Chippewa alone","Choctaw alone","Comanche alone","Creek alone","Crow alone","Hopi alone","Iroquois alone","Lumbee alone","Mexican American Indian alone","Navajo alone","Pima alone","Potawatomi alone","Pueblo alone","Puget Sound Salish alone","Seminole alone","Sioux alone","South American Indian alone","Tohono O'Odham alone","Yaqui alone","Other specified American Indian tribes alone","All other specified American Indian tribe combinations","American Indian, tribe not specified","Alaskan Athabascan alone","Tlingit-Haida alone","Inupiat alone","Yup'ik alone","Aleut alone","Other Alaska Native","Other American Indian and Alaska Native specified","American Indian and Alaska Native, not specified","Asian Indian alone","Bangladeshi alone","Bhutanese alone","Burmese alone","Cambodian alone","Chinese, except Taiwanese, alone","Taiwanese alone","Filipino alone","Hmong alone","Indonesian alone","Japanese alone","Korean alone","Laotian alone","Malaysian alone","Mongolian alone","Nepalese alone","Pakistani alone","Sri Lankan alone","Thai alone","Vietnamese alone","Other Asian alone","All combinations of Asian races only","Native Hawaiian alone","Samoan alone","Tongan alone","Guamanian or Chamorro alone","Marshallese alone","Fijian alone","Other Native Hawaiian and Other Pacific Islander","Some Other Race alone","Two or More Races"))

df$ST<-factor(df$ST,levels=c(1,2,4,5,6,8,9,10,11,12,13,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,44,45,46,47,48,49,50,51,53,54,55,56,72),
labels=c("AL","AK","AZ","AR","CA","CO","CT","DE","DC","FL","GA","HI","ID","IL","IN","IA","KS","KY","LA","ME","MD","MA","MI","MN","MS","MO","MT","NE","NV","NH","NJ","NM","NY","NC","ND","OH","OK","OR","PA","RI","SC","SD","TN","TX","UT","VT","VA","WA","WV","WI","WY","PR"))

df$LANP<-factor(df$LANP,levels=c(1000,1025,1055,1069,1110,1120,1125,1130,1132,1134,1140,1141,1142,1155,1170,1175,1200,1210,1220,1231,1235,1242,1250,1260,1262,1263,1270,1273,1274,1275,1276,1277,1278,1281,1283,1288,1290,1292,1315,1327,1340,1350,1360,1380,1420,1435,1440,1450,1500,1525,1530,1540,1564,1565,1582,1675,1690,1730,1737,1750,1765,1900,1960,1970,2000,2030,2050,2100,2160,2270,2350,2430,2475,2525,2535,2560,2575,2715,2770,2850,2910,2920,2950,3150,3190,3220,3270,3350,3420,3500,3570,3600,4500,4545,4560,4565,4590,4640,4830,4840,4880,4900,5150,5345,5525,5645,5845,5900,5940,5950,6120,6205,6230,6290,6300,6370,6500,6795,6800,6839,6930,6933,6936,7019,7032,7039,7050,7059,7060,7124,7300,9999), labels=c("Jamaican Creole English","Other English-based Creole languages","Haitian","Kabuverdianu","German","Swiss German","Pennsylvania German","Yiddish","Dutch","Afrikaans","Swedish","Danish","Norwegian","Italian","French","Cajun French","Spanish","Portuguese","Romanian","Irish","Greek","Albanian","Russian","Ukrainian","Czech","Slovak","Polish","Bulgarian","Macedonian","Serbocroatian","Bosnian","Croatian","Serbian","Lithuanian","Latvian","Armenian","Farsi","Dari","Kurdish","Pashto","India N.E.C.","Hindi","Urdu","Bengali","Punjabi","Konkani","Marathi","Gujarati","Nepali","Pakistan N.E.C.","Sinhala","Other Indo-Iranian languages","Other Indo-European languages","Finnish","Hungarian","Turkish","Mongolian","Telugu","Kannada","Malayalam","Tamil","Khmer","Vietnamese","Chinese","Mandarin","Min Nan Chinese","Cantonese","Tibetan","Burmese","Chin languages","Karen languages","Thai","Lao","Iu Mien","Hmong","Japanese","Korean","Malay","Indonesian","Other languages of Asia","Filipino","Tagalog","Cebuano","Ilocano","Other Philippine languages","Chamorro","Marshallese","Chuukese","Samoan","Tongan","Hawaiian","Other Eastern Malayo-Polynesian languages","Arabic","Hebrew","Assyrian Neo-Aramaic","Chaldean Neo-Aramaic","Amharic","Tigrinya","Oromo","Somali","Other Afro-Asiatic languages","Nilo-Saharan languages","Swahili","Ganda","Shona","Other Bantu languages","Manding languages","Other Mande languages","Fulah","Wolof","Akan (incl. Twi)","Ga","Gbe languages","Yoruba","Edoid languages","Igbo","Other Niger-Congo languages","Other languages of Africa","Aleut languages","Ojibwa","Apache languages","Navajo","Kiowa-Tanoan languages","Dakota languages","Muskogean languages","Keres","Cherokee","Zuni","Uto-Aztecan languages","Other Native North American languages","Other Central and South American languages","Other and unspecified languages"))
```

# Data Summary

I choose to analyse population characteristics from the ACS data set, I thought it would be interesting to compare people from different Races and compare people within a particular race. Some of the columns that I picked are Age, Sex, Marital Status, Ability to speak English, Educational qualifications, Race, Income, Language spoken at home and type of Citizenship.

#1. Age group break-up
To get a sense of the age distribution, I divided the age column into 4 groups Children, Youth, Adults and Seniors. A large fraction of the population, approximately 55% comprises of adults aged between (25-64 years), children form the next largest group followed by seniors and youth which represent the minority in the data set. I decided to explore attributes only for people aged between 25 and 64 years. 
```{r}
#Age Group Distribution
ggplot(data = df)+geom_bar(mapping = aes(x = agegroup, weight=PWGTP/sum(PWGTP)*100, fill = agegroup))+labs(title= "Break-up of Age Groups", x="Age Groups", y="Percentage %")+scale_fill_discrete(name="Age Groups",             breaks=c("Adult","Children","Senior","Youth"),labels=c("Adults(25-64 yrs)","Children(0-14 yrs)","Senior(65+ yrs)", "Youth(15-24 yrs)"))
```

#2. Proportion of Races
The next attribute that I picked is the Race attribute, I wanted to see how people performed in terms of income and education among different races and also identify races that earn the highest incomes with respect to other races. Below is a break-up of the 9 main races represented in the dataset. The top 3 races that form the population are Whites, Blacks and Asians. As, can be seen from the table Whites form the majority of the population comprising nearly 73% of the population, followed by Blacks which make up 12.6% of the population and Asians which account for 5.2% of the population.
```{r}
#Weighted Proportion of Races based on the first Race entry 
tab<-wpct(df$RAC1P, weight=df$PWGTP)

#Converting to a data frame and tabulating the results
Prop_race<-data.frame(Race=names(tab), Proportion=as.numeric(tab))%>%arrange(desc(Proportion))
kable(Prop_race)%>%kable_styling(bootstrap_options = c("striped", "hover"),font_size = 14)%>%
row_spec(0, bold = T, color = "white", background = "purple")
```


#3. English Speaking Ability
I thought it was worth noting how the ability to speak English has an impact on the Income. Below is a bar chart representing the number of people and their levels of English proficiency only for people aged between 25 to 64 years. Most of the people in the data set are able to speak English well.
```{r}
x<-df%>%filter(agegroup=="Adult"&!is.na(ENG))%>%group_by(ENG)%>%summarise(count=sum(PWGTP))

ggplot(x, aes(x=ENG, y=count, fill=ENG))+geom_bar(stat="identity")+theme_light()+
scale_fill_manual(values=c("plum4", "plum3", "plum2","plum1"))+labs(title= "Ability to speak English", x="English Proficiency", y="No. of people", name="Proficiency")+theme(legend.position="none")
```

#4. Income Distribution
The below histogram gives a idea of the income distribution for Adults (25-64 years). Most people earn between 0-50k as indicated by red, as the income increases there is a decrease in the number of people. We can clearly see that there are fewer people earning incomes greater than $50k.
```{r}
p<-df%>%filter(agegroup=="Adult" & !is.na(PINCP))
ggplot(data=p, aes(p$PINCP,weight=PWGTP)) + 
geom_histogram(breaks=seq(2000,200000, by =2000), col="red", aes(fill=..count..))+
labs(title= "Income Distribution", x="Income", y="No. of people")+
scale_fill_gradient("No. of people", low = "green", high ="red")
```

#5. State-Wise Income Distribution 

The below Choropleth depicts how the average income is spread across different states in the US. The states of Maryland and Connecticut have higher incomes in comparision to any of the other states, on the other hand the states of West Virginia, Mississippi and Arkansas have the lowest average incomes. 
```{r}
#State wise income distribution
a<-df%>%filter(agegroup=="Adult"&!is.na(PINCP))%>%group_by(ST)%>%summarise(State_Income=weighted.mean(PINCP,PWGTP))

hcmap("countries/us/us-all", data = a, name = "Average Income", value = "State_Income", joinBy = c("hc-a2", "ST"), borderColor = "transparent", dataLabels = list(enabled = TRUE, format = '{point.name}'))%>%
hc_colorAxis(dataClasses = color_classes(c(seq(30000, 60000, by = 5000))))%>%
hc_legend(layout = "vertical", align = "right",floating = TRUE, valueDecimals = 0)%>%
hc_title(text = "<b>State-wise Income Distribution</b>", align = "center", color = "black",valueSuffix = "$")


```

#6. Education Qualifications
The below bar plot identifies the top 10 educational attainments for men and women between 25 and 64 years in the population. It turns out that most of the Men in the population only have a regular High school diploma. On the other hand, more women have a Bachelor's degree, Associate Degree and Master's Degreee in comparison to men, which means that women have higher educational qualifications than men.
```{r}
x<-df%>%filter(agegroup=="Adult")%>%group_by(SEX,SCHL)%>%summarise(count=sum(PWGTP))%>%arrange(desc(count))%>%top_n(10)

hchart(x, type="bar", hcaes(x = SCHL, y=count, group=SEX))%>%
hc_xAxis(title = list(text = "<b>Educational Attainment<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>No. of people<b>"), color="black")%>%
hc_title(text = "<b>Top 10 Educational Attainments</b>", align = "center", color = "black")
```

#7. Comparison of marital status among Men and Women
It appears that most of the people in the population aged between 25-64 years are married, approximately equal number of men and women are married, however there are more single men and than women. The number of people widowed, divorced or separated only account for a small fraction of the population. Also, more women tend to be divorced widowed or separated in comparison to men.
```{r}
library(highcharter)
myColors <- c("#002F80", "pink")
x<-df%>%filter(agegroup=="Adult")%>%group_by(SEX,MAR)%>%summarise(count=sum(PWGTP))

hchart(x, type="column", hcaes(x = MAR, y=count , group = SEX))%>%
hc_xAxis(title = list(text = "<b>Marital Status<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>No. of People<b>"), color="black")%>%
hc_colors(myColors)%>%
hc_title(text = "<b>Marital Status vs Gender</b>", align = "center", color = "black")
```

# Methodology

There were many relationship to be explored between the different variables.

#1. Income VS gender VS races
I began by comparing the average incomes earned among different races. After comparing the income for all the 9 major races and for gender within each race, the Asian race stood out, on average Asians earn more than any of the other races, in terms of gender men on average earn more than women. The top 2 earning races are Asians and Whites as depcited by the bar plot I further went on to compare the educational attainments and English speaking ability between these 2 races. 

```{r}
x<-df%>%filter(agegroup=="Adult")%>%group_by(SEX,RAC1P)%>%summarise(Average_Income=weighted.mean(PINCP,PWGTP))%>%arrange(desc(Average_Income))

hchart(x, type="column", hcaes(x = RAC1P, y=Average_Income, group=SEX))%>%
hc_xAxis(title = list(text = "<b>Educational Attainment<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>Income<b>"), color="black")%>%
hc_title(text = "<b>Income vs Race vs Gender</b>", align = "center", color = "black")%>%
hc_add_theme(hc_theme_sandsignika())
```

#2. Educational Attainment vs Income
I thought of comparing the how the educational qualification affects the income, quite obviously people with higher levels of education tend to earn more. Men on average earn more than women, people with a professional degree beyond a bachelor's degree make more money that those people holding a Doctorate degree or Master's degree.
```{r}
x<-df%>%filter(agegroup=="Adult")%>%group_by(SEX,SCHL)%>%summarise(Avg_inc=weighted.mean(PINCP, PWGTP))%>%arrange(desc(Avg_inc))%>%top_n(10)

hchart(x, type="bar", hcaes(x = SCHL, y=Avg_inc, group=SEX))%>%
hc_xAxis(title = list(text = "<b>Educational Attainment<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>Income<b>"), color="black")%>%
hc_title(text = "<b>Income vs Educational Qualifications vs Gender</b>", align = "center", color = "black")%>%
hc_add_theme(hc_theme_flat())
```

#3. Income VS race vs eng ability
I compared the income earned for the races that make the most income i.e Asians and Whites with respect to their ability to speak English. It turns out that Asians that speak English well earn more on average than Whites.
The ability to speak English well affects the income, from the below bar plot you can see that as the English proficiency decreases the average income also decreases. Thus there is a clear trend between income and English proficiency people with higher levels of proficiency tend to earn more.
```{r}
myColors <- c("#002F80", "#F9AF38")
x<-df%>%filter((RAC1P=="Asian alone" | RAC1P=="White alone") & agegroup=="Adult" & !is.na(ENG))%>%group_by(RAC1P,ENG)%>%summarise(Avg_inc=weighted.mean(PINCP,PWGTP))

hchart(x, type="column", hcaes(x = ENG, y=Avg_inc, group=RAC1P))%>%
hc_xAxis(title = list(text = "<b>Ability to speak English<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>Income<b>"), color="black")%>%
hc_colors(myColors)%>%
hc_title(text = "<b>Income vs Race for top 2 earning races</b>", align = "center", color = "black")

```


#4. Income among the Asian race
I decided identify which Asians earn more income on average within the Asian race. It turns out that Indians earn more than any of the other groups.
```{r}
df%>%filter(RAC1P=="Asian alone" & agegroup=="Adult")%>%group_by(RAC2P)%>%summarise(Avg_inc=weighted.mean(PINCP,PWGTP))%>%mutate(RAC2P= reorder(RAC2P, Avg_inc))%>%top_n(10)%>%ggplot(aes(RAC2P, Avg_inc, fill=RAC2P))+geom_bar(stat = "identity")+theme(legend.position="none")+coord_flip()+labs(title= "Top 10 earning Asian Races", x="Race", y="Average Income")
```
# Proportion of Indians within the Asian Race
```{r}
#Filtering for only Asian races
asian<-df%>%filter(RAC1P=="Asian alone"&agegroup=="Adult")%>%group_by(RAC2P)
tab<-wpct(asian$RAC2P, weight=asian$PWGTP)

#Tabulating the proportion of top 10 Asians in USA
Prop_Asian_race<-data.frame(Race=names(tab), Proportion=as.numeric(tab))%>%arrange(desc(Proportion))%>%top_n(10)
kable(Prop_Asian_race)%>%kable_styling(bootstrap_options = c("striped", "hover"),font_size = 14)%>%
row_spec(0, bold = T, color = "white", background = "purple")%>%
row_spec(2, bold = T, color = "black", background = "plum")
```

##5. Education indians alone
Since Indians earn more than any of the other Asian races, I thought it was worth checking the top 4 educational attainments for Indians. Most of the Indians have either a Bachelor's degree or a Master's degree with more men pursuing a master's degree than women.
```{r}
x<-df%>%filter(RAC2P=="Asian Indian alone"& agegroup=="Adult")%>%group_by(SEX,SCHL)%>%summarise(count=sum(PWGTP))%>%arrange(desc(count))%>%top_n(4)
hchart(x, type="bar", hcaes(x = SCHL, y=count, group=SEX))%>%
hc_xAxis(title = list(text = "<b>Educational Attainment<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>No. of people<b>"), color="black")%>%
hc_title(text = "<b>Top 4 Eductional Attainments among Indians</b>", align = "center", color = "black")%>% hc_add_theme(hc_theme_elementary())
```

#6. Educational Attainment for Whites
Among the Whites most of them have a Regular high school diploma or Bachelor's degree with more women pursuing a Bachelor's degree than men.
```{r}
x<-df%>%filter(RAC1P=="White alone"& agegroup=="Adult")%>%group_by(SEX,SCHL)%>%summarise(count=sum(PWGTP))%>%arrange(desc(count))%>%top_n(4)
hchart(x, type="bar", hcaes(x = SCHL, y=count, group=SEX))%>%
hc_xAxis(title = list(text = "<b>Educational Attainment<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>No. of people<b>"), color="black")%>%
hc_title(text = "<b>Top Eductional Attainments among Whites</b>", align = "center", color = "black")%>% 
hc_add_theme(hc_theme_ffx())
```

#7. Multi-facetted plot to compare educational attainment between Whites and Asians
```{r}

df%>%filter(agegroup=="Adult" & (RAC2P=="Asian Indian alone" | RAC2P=="White alone"))%>%group_by(RAC2P,SCHL)%>%summarise(count=sum(PWGTP))%>%mutate(SCHL = reorder(SCHL,count))%>%top_n(4)%>%ggplot(aes(SCHL, count, fill = RAC2P)) +geom_col(show.legend = FALSE) +labs(x = NULL, y = "No. of people") + facet_wrap(~RAC2P, ncol = 2, scales = "free")+ theme(axis.text.x = element_text(angle=45, hjust=1))
```
#4. Multi-facetted plot English proficiency of Indians based on the type of Citizenship 
```{r}

df%>%filter(agegroup=="Adult" & RAC2P=="Asian Indian alone" & !is.na(ENG))%>%group_by(CIT,ENG)%>%summarise(count=sum(PWGTP))%>% mutate(ENG = reorder(ENG,count))%>%ggplot(aes(ENG, count, fill = CIT)) +geom_col(show.legend = FALSE) +labs(x = NULL, y = "No. of people") + facet_wrap(~CIT, ncol = 2, scales = "free") +coord_flip()
```

#7. Income based on educational attainments for Indians
People with a professional degree beyond Bachelor's earn more than any of the other 3 groups.

```{r}
x<-df%>%filter(RAC2P=="Asian Indian alone"& agegroup=="Adult" & (SCHL=="Doctorate degree"|SCHL=="Bachelor's degree"|SCHL=="Master's degree"|SCHL=="Professional degree beyond a bachelor's degree"))%>%group_by(SEX,SCHL)%>%summarise(inc=weighted.mean(PINCP,PWGTP))

hchart(x, type="column", hcaes(x = SCHL, y=inc, group=SEX))%>%
hc_xAxis(title = list(text = "<b>Educational Attainment<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>Income<b>"), color="black")%>%
hc_title(text = "<b>Income earned based on Educational Degree</b>", align = "center", color = "black")%>% hc_add_theme(hc_theme_google())
```

#Wanted to see the occupation of those with professional degree beyond bachelor's
```{r}
x<-df%>%filter(RAC2P=="Asian Indian alone"& agegroup=="Adult" & (SCHL=="Doctorate degree"|SCHL=="Bachelor's degree"|SCHL=="Master's degree"|SCHL=="Professional degree beyond a bachelor's degree"))%>%group_by(SEX,SCHL)%>%summarise(inc=weighted.mean(PINCP,PWGTP))
x
```
## Boxplot Educational Levels
```{r}
#Boxplot Income vs Education levels
g <- ggplot(x, aes(SCHL, inc))
g + geom_boxplot(varwidth=T, fill="plum") + 
    labs(title="Boxplot of Income for 4 different levels of education", 
         x="Educational Attainment",
         y="Income")+coord_flip()

```

```{r}
x<-df%>%filter((RAC1P=="Asian alone" | RAC1P=="White alone") & agegroup=="Adult" & !is.na(ENG))%>%group_by(RAC1P,ENG)%>%summarise(Avg_inc=weighted.mean(PINCP,PWGTP))

#Income vs Education levels
g <- ggplot(df, aes(ENG, PINCP))
g + geom_boxplot(varwidth=T, fill="plum", outlier.shape = NA) + 
    labs(title="Boxplot of Income for 4 different levels of education", 
         x="Educational Attainment",
         y="Income")+coord_flip()
```


#8. Most frequent languages spoken at home by Indians in the US
```{r}
df%>%filter(RAC1P=="Asian alone" & RAC2P=="Asian Indian alone" & !is.na(LANP))%>%group_by(LANP)%>%summarise(y=sum(PWGTP))%>%arrange(desc(y))%>%top_n(10)%>%with(wordcloud(LANP, y, max.words = 10))
```

#9. Mean Income within the Indian community
```{r}
df%>%filter(RAC1P=="Asian alone" & RAC2P=="Asian Indian alone" & !is.na(LANP))%>%group_by(LANP)


#%>%summarise(Mean_Inc=weighted.mean(PINCP,PWGTP))%>%arrange(desc(Mean_Inc))%>%top_n(10)

#%>%with(wordcloud(LANP, y, max.words = 10))
```


```{r}
#Distribution of Indians across the US
ind_dis<-df%>%filter(agegroup=="Adult"&RAC2P=="Asian Indian alone")%>%group_by(ST)%>%summarise(count=sum(PWGTP))
ind_dis
hcmap("countries/us/us-all", data = ind_dis, name = "No. of Indians", value = "count", joinBy = c("hc-a2", "ST"), borderColor = "transparent",dataLabels = list(enabled = TRUE, format = '{point.name}'))%>%
hc_colorAxis(dataClasses = color_classes(c(seq(0,100000, by = 20000),500000)))%>%
hc_legend(layout = "vertical", align = "right",floating = TRUE, valueDecimals = 0)%>%
hc_title(text = "<b>Distribution of Indians across the US</b>", align = "center", color = "black",valueSuffix = "$")
```


# Average Income earned by Indians across different states in the US
```{r}
#Average income earned by Indians across the USA
avg_inc_ind<-df%>%filter(agegroup=="Adult"&RAC2P=="Asian Indian alone")%>%group_by(ST)%>%summarise(Avg_inc=weighted.mean(PINCP,PWGTP))

hcmap("countries/us/us-all", data = avg_inc_ind, name = "No. of Indians", value = "Avg_inc", joinBy = c("hc-a2", "ST"), borderColor = "transparent",dataLabels = list(enabled = TRUE, format = '{point.name}'))%>%
hc_colorAxis(dataClasses = color_classes(c(seq(20000,80000, by = 10000),150000)))%>%
hc_legend(layout = "vertical", align = "right",floating = TRUE, valueDecimals = 0,valueSuffix = "$")%>%
hc_title(text = "<b>State-wise Average Income earned by Indians</b>", align = "center", color = "black",valueSuffix = "$")
```

# Income earned vs age vs marital status
```{r}
m<-df%>%filter(agegroup=="Adult")%>%group_by(MAR,AGEP)%>%summarise(Avg_inc=weighted.mean(PINCP,PWGTP))

hchart(m, type="scatter", hcaes(x = AGEP, y = Avg_inc, group = MAR))%>%
hc_title(text = "<b>Income vs Age vs Marital Status</b>", align = "center", color = "black")%>%
hc_xAxis(title = list(text = "<b>Age<b>", color="black"))%>%
hc_yAxis(title = list(text = "<b>Income<b>"), color="black")
```

#### Linear regression model
```{r}
indians<-df%>%filter(RAC2P=="Asian Indian alone"&agegroup=="Adult")
model<-lm(PINCP~SEX+(SCHL=="Bachelor's degree")+(SCHL=="Master's degree")+(SCHL=="Professional degree beyond a bachelor's degree")+(SCHL=="Doctorate degree")+ENG, data=indians)
summary(model)
```

```{r}
hist(indians$PINCP)

```
